### 2016-05-02 ch03-lrm/nonparametric.tex
Move LPM illustration

In these expressions, we denote $\LocalModel[k]{G}$ and $\LocalModel[k]{T}$ for the local model for respectively transfer function and the transient.
Note that such local quantities (which depend on the frequency bin $k$) are denoted in bold.
To alleviate the notations, the subscript $k$ is omitted unless

@@

Note that the estimated \gls{FRF} is given by evaluating the local model $\LocalModel{G}$:
\begin{equation}
  \hat{G}_{\LRIC}(\omega_k) \isdef \LocalModel[k]{G}(d=0)
  \text{.}
\end{equation}

\begin{remark}
It should be noted that \eqref{eq:LRM:model:G} and \eqref{eq:LRM:model:T} are essentially isomorphic to a continuous-time transfer function model with complex coefficients.
The discrete-time counterparts (i.e. substituting $d^i \to \exp (ji d \Ts)$ in the expressions), have been tried as well.
However, these preliminary experiments did not yield estimates that were numerically reliable.
\end{remark}

\subsection{The Local Rational Method}
\label{sec:nparam:LRM}
The \gls{LRM} as first introduced in \citet{McKelvey2012LRM}, overcomes the computational burden of an iterative procedure by weighting the equation error by the denominator polynomial $\LocalModel{A}$  akin to the procedure in \citep{Levy1959}.
I.e. the \gls{LRM} procedure tries to minimize the equation error in
\begin{equation}
  \LocalModel{A} \hadamard \LocalVector{Y} = \LocalModel{B} \hadamard \LocalVector{U}  + \LocalVector{C} + \LocalVector{V}
  \text{,}
\end{equation}
for which the corresponding cost function is
\begin{equation}
  \LocalVector{\CostFunc{\LRM}}
  \isdef 
  \left( \LocalModel{A} \hadamard \LocalVector{Y}  -  \LocalModel{B} \hadamard \LocalVector{U} - \LocalModel{C} \right)^{\HT} 
      \left( \LocalModel{A} \hadamard \LocalVector{Y}  -  \LocalModel{B} \hadamard \LocalVector{U} - \LocalModel{C} \right)
      \text{.}
      \label{eq:nparam:LRM:costFunc}
\end{equation}
where $\LocalVector{V}$ is vector consisting of \gls{iid} complex normally distributed variables~\citep{Gallager2008} that each have a variance $\sigma_V^2$, i.e. the disturbing noise is assumed white over the local frequency window.
Equivalently, the last equation can be rewritten as a linear regression problem
\begin{equation}
  \LocalVector{Y} = \LocalMatrix{K} \LocalVector{\theta} + \LocalVector{V}
  \label{eq:nparam:linearRegression}
\end{equation}
where $\LocalMatrix{K}$ is the so-called design matrix (or observation matrix):
\begin{align}
  \label{eq:nparam:designMatrix}
  \LocalMatrix{K} 
    & \isdef 
    \phantom{+}
  \mat{
     \LocalMatrix{K}_A &
     \LocalMatrix{K}_B & 
     \LocalMatrix{K}_C
  }\\
  \LocalMatrix{K}_A 
    &\isdef
    \phantom{+}
    \mat{
      \LocalVector{Y} \hadamard \LocalVector{d}^1 &
      \cdots &
      \LocalVector{Y} \hadamard \LocalVector{d}^{\order{A}}
    }\\
  \LocalMatrix{K}_B 
    &\isdef
    - \mat{
      \LocalVector{U} \hadamard \LocalVector{d}^0 &
      \cdots &
      \LocalVector{U} \hadamard \LocalVector{d}^{\order{B}}
    }\\
  \LocalMatrix{K}_C
    &\isdef
    - \mat{
      \LocalVector{d}^0 &
      \cdots &
      \LocalVector{d}^{\order{C}}
    }
    \text{.}
\end{align}
In this formulation, we have used $\LocalVector{d}^{n}$ to denote the $n^{\text{th}}$ Hadamard power of $\LocalVector{d}$ (this corresponds to \mcode{d.^n} in \MATLAB) such that
\begin{equation}
    \LocalVector{d}^{n} 
    \isdef
    \mat{
      (-\numel{W})^{n} &
      \cdots &
      (\numel{W})^{n}
    }^{\T}
    \text{ with $n \in \mathbb{Z}$}
\end{equation}
where every element corresponds to a value of $d^{n}$ in accordance with $\LocalShifts{k}$.

>>>>

In these expressions, we denote $\LocalModel[k]{G}$ and $\LocalModel[k]{T}$ for the local model for respectively transfer function and the transient.
Note that such local quantities (which depend on the frequency bin $k$) are denoted in bold.
To alleviate the notations, the subscript $k$ is omitted whenever this does not cause ambiguity.

@@

Note that the estimated \gls{FRF} is given by evaluating the local model $\LocalModel{G}$:
\begin{equation}
  \hat{G}_{\LRIC}(\omega_k) \isdef \LocalModel[k]{G}(d=0)
  \text{.}
\end{equation}
In \figref{fig:nparam:illustration}, the local window $\LocalWindow[k]$, the local input-output spectra ($\LocalVector[k]{U}$ and $\LocalVector[k]{U}$) are illustrated.

\begin{figure}[htb] %  figure placement: here, top, bottom, or page
   \centering
   \setlength{\figurewidth}{0.8\columnwidth}
   \setlength{\figureheight}{0.68\figurewidth}
   \input{\thisDir/figs/LPMfig.tikz}
   \caption[Illustration of local modeling.]{Illustration of local modeling. Top figures: input spectrum (left) and output spectrum (right). 
   A small frequency window $\LocalWindow[k]$ is selected, in which the local model $\LocalModel[k]{G}$ is estimated. Its central value $\hat{G}(\omega_k)$ is an estimate of the \gls{FRF}. This procedure is repeated for all frequencies $\omega_k$. \disclaimer{Figure based on \citep[Fig.~2]{Lumori2014TIM}.}}
   \label{fig:nparam:illustration}
\end{figure}

\begin{remark}
It should be noted that \eqref{eq:LRM:model:G} and \eqref{eq:LRM:model:T} are essentially isomorphic to a continuous-time transfer function model with complex coefficients.
The discrete-time counterparts (i.e. substituting $d^i \to \exp (ji d \Ts)$ in the expressions), have been tried as well.
However, these preliminary experiments did not yield estimates that were numerically reliable.
This is in correspondence with the remark from \citet{Pintelon2006BJ1}.
\end{remark}

\subsection{The Local Rational Method}
\label{sec:nparam:LRM}
The \gls{LRM} as first introduced by \citet{McKelvey2012LRM}, overcomes the computational burden of an iterative procedure by weighting the equation error by the denominator polynomial $\LocalModel{A}$  akin to the procedure in \citep{Levy1959}.
I.e. the \gls{LRM} procedure tries to minimize the equation error in
\begin{equation}
  \LocalModel{A} \hadamard \LocalVector{Y} = \LocalModel{B} \hadamard \LocalVector{U}  + \LocalVector{C} + \LocalVector{V}
  \text{,}
\end{equation}
for which the corresponding cost function is
\begin{equation}
  \LocalVector{\CostFunc{\LRM}}
  \isdef 
  \left( \LocalModel{A} \hadamard \LocalVector{Y}  -  \LocalModel{B} \hadamard \LocalVector{U} - \LocalModel{C} \right)^{\HT} 
      \left( \LocalModel{A} \hadamard \LocalVector{Y}  -  \LocalModel{B} \hadamard \LocalVector{U} - \LocalModel{C} \right)
      \text{.}
      \label{eq:nparam:LRM:costFunc}
\end{equation}
where $\LocalVector{V}$ is vector consisting of \gls{iid} complex normally distributed variables~\citep{Gallager2008} that each have a variance $\sigma_V^2$, i.e. the disturbing noise is assumed white over the local frequency window.
Equivalently, the last equation can be rewritten as a linear regression problem
\begin{equation}
  \LocalVector{Y} = \LocalMatrix{K} \LocalVector{\theta} + \LocalVector{V}
  \label{eq:nparam:linearRegression}
\end{equation}
where $\LocalMatrix{K}$ is the so-called design matrix (or observation matrix):
\begin{align}
  \label{eq:nparam:designMatrix}
  \LocalMatrix{K} 
    & \isdef 
    \phantom{+}
  \mat{
     \LocalMatrix{K}_A &
     \LocalMatrix{K}_B & 
     \LocalMatrix{K}_C
  }\\
  \LocalMatrix{K}_A 
    &\isdef
    \phantom{+}
    \mat{
      \LocalVector{Y} \hadamard \LocalVector{d}^1 &
      \cdots &
      \LocalVector{Y} \hadamard \LocalVector{d}^{\order{A}}
    }\\
  \LocalMatrix{K}_B 
    &\isdef
    - \mat{
      \LocalVector{U} \hadamard \LocalVector{d}^0 &
      \cdots &
      \LocalVector{U} \hadamard \LocalVector{d}^{\order{B}}
    }\\
  \LocalMatrix{K}_C
    &\isdef
    - \mat{
      \LocalVector{d}^0 &
      \cdots &
      \LocalVector{d}^{\order{C}}
    }
    \text{.}
\end{align}
In this formulation, we have used $\LocalVector{d}^{n}$ to denote the $n^{\text{th}}$ Hadamard power of $\LocalVector{d}$ (this corresponds to \mcode{d.^n} in \MATLAB) such that
\begin{equation}
    \LocalVector{d}^{n} 
    \isdef
    \mat{
      (-\numel{W})^{n} &
      \cdots &
      (\numel{W})^{n}
    }^{\T}
    \text{ with $n \in \mathbb{Z}$}
\end{equation}
where every element corresponds to a value of $d^{n}$ in accordance with $\LocalShifts{k}$.
